Ecological Importance of Smooth Brome in Managing Wheat Stem Sawfly (Hymenoptera: Cephidae) via Its Associated Braconid Parasitoids

### 2024-05-17 qmd/projects/msu/wss/paper1.rmd
updated linked papers

---
title: "Ecological Importance of Smooth Brome in Managing Wheat Stem Sawfly (Hymenoptera: Cephidae) via Its Associated Braconid Parasitoids"
authors: "Jackson R. Strand, David K. Weaver"
date: "May 14, 2024"
editor_options: 
  chunk_output_type: console
bibliography: proposal.bib
link-citations: true
biblio-style: apalike
cls: 
  max-names: 1
---

This document can be downloaded as either a .docx or .pdf document. Please be aware that conversion may cause the formatting to be altered.

@@

@@

### Figure 1 {#figure1}
```{r FIG1_both_prcp_plot, fig.width = 10, out.width = '100%', fig.align = 'left', fig.cap = "Figure 1: Average yearly precipitation (in) for Big Sandy and Moccasin, Montana. Black trend line signifies averaged negative trend between both locations. Data gathered from NOAA and MSU-ARS. A significant linear relationship (r = 0.1, P = 0.033, estimate = -0.058) was observed between year and average yearly precipitation."}
both_prcp_plot 
```

### Figure 2 {#figure2}
```{r both_temp_plot, fig.width = 10, fig.align = 'left', fig.cap = "Figure 2: Average yearly temperature (°C) in Moccasin and Big Sandy, MT. Positive trendline slop suggests increasing average temperatures of the past 100 years. A significant linear relationship (*r =0.2447, P < 0.05, estimate = 0.028*) was observed between year and average yearly temperature."}
both_temp_plot
```

### Figure 3 {#figure3}
```{r bs_ndvi_plot, fig.align = 'left', fig.cap = "Figure 3: Normalized difference vegetation index (NDVI) of *B. inermis* and adjacent spring wheat field from April 2023 to October 2023. Post harvest linear model indicates a significant difference (P values and stuff) when comparing the *B. inermis* post-harvest slope and the spring wheat post-harvest slope."}
bs_ndvi_plot
```

>>>>

---
title: "Ecological Importance of Smooth Brome in Managing Wheat Stem Sawfly (Hymenoptera: Cephidae) via Its Associated Braconid Parasitoids"
authors: "Jackson R. Strand, David K. Weaver"
date: "May 17, 2024"
editor_options: 
  chunk_output_type: console
bibliography: paper1.bib
link-citations: true
biblio-style: apalike
cls: 
  max-names: 1
---
<div class="box">
This document can be downloaded as either a .docx or .pdf document. Please be aware that conversion may cause the formatting to be altered.

@@

</div>

@@

### Figure 1 {#figure1}
```{r FIG1_both_prcp_plot, fig.cap = "Figure 1: Average yearly precipitation (in) for Big Sandy and Moccasin, Montana. Black trend line signifies averaged negative trend between both locations. Data gathered from NOAA and MSU-ARS. A significant linear relationship (r = 0.1, P = 0.033, estimate = -0.058) was observed between year and average yearly precipitation."}
both_prcp_plot 
```

### Figure 2 {#figure2}
```{r both_temp_plot, fig.cap = "Figure 2: Average yearly temperature (°C) in Moccasin and Big Sandy, MT. Positive trendline slop suggests increasing average temperatures of the past 100 years. A significant linear relationship (*r =0.2447, P < 0.05, estimate = 0.028*) was observed between year and average yearly temperature."}
both_temp_plot
```

### Figure 3 {#figure3}
```{r bs_ndvi_plot, fig.cap = "Figure 3: Normalized difference vegetation index (NDVI) of *B. inermis* and adjacent spring wheat field from April 2023 to October 2023. Post harvest linear model indicates a significant difference (P values and stuff) when comparing the *B. inermis* post-harvest slope and the spring wheat post-harvest slope."}
bs_ndvi_plot
```
